Object naming is context-dependent - A case study on testing linguistic hypotheses on real-world image corpora

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
revising

For instance, if we want to check whether a specific object like \cat{convertible} is more often referred to with a basic-level category (e.g.,~\refexp{car}) or a more specific one (e.g.,~\refexp{convertible, limousine}), all three requirements need to be fulfilled: we need to know whether the object is a \cat{convertible} or a \cat{limousine}, and likewise for its distractors, and we need to know wether a speaker called the object that \refexp{convertible, car, etc}.

>>>>

%For instance, if we want to find out whether a specific object like \cat{convertible} is more often referred to with a basic-level category (e.g.,~\refexp{car}) or a more specific one (e.g.,~\refexp{convertible, limousine}), all three requirements need to be fulfilled: we need to know whether the object is a \cat{convertible} or a \cat{limousine}, and likewise for its distractors, and we need to know whether a speaker called the object \refexp{convertible, car, etc}.

For instance, if we want to find out whether a specific object like the left dog in  Fig.~\ref{fig:graf_genome}, second-left image, is more often referred to with a basic-level category (e.g.,~\refexp{dog}) or a more specific one (e.g.,~\refexp{dalmatian}), all three requirements need to be fulfilled: we need to know whether the object is a \cat{dalmatian} or, e.g.,~an \cat{irish setter}, and likewise for its distractors, and we need to know whether a speaker called the object \refexp{dalmatian, dog, etc}.
